---
title: "Sturge Method - Equal Intervals"
author: "Ravindra Reddy Tamma"
date: "29 July 2018"
output: rmarkdown::github_document
#output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
STURGE FORMULA (or) METHOD : 
    It is used to divide the raw data given in the form of a vector in to class intervals of equal widths. The Method Implemented in R can directly identify the suitable number of Class Intervals and also allocate appropriate width for each class.
    
No.of Classes is defined using:
k = log(n,base = 2) # K = No.of Classes and n = length of the vector

Width of each interval is defined using:
w = (High + Low)/k # High = Maximum Value and Low = Minimum value

```{r}
# STRUGE Formula to make equal intervals for Data.

sturge <- function(vect)
{
  if(class(vect) == "character")
    return(transform(table(vect)))
  n <- length(vect)
  if(n == 1)return(table(vect))
  low <- round(min(vect,na.rm = TRUE))
  high <- round(max(vect,na.rm = TRUE))
  k <- round(log2(n))
  width <- round((high - low)/k)
  if(width > 0)
  {
    bins <- seq(low,high+width,width)
  }
  else
  {
    stop("Width of Interval is not Correct or NA values in DataSet")
  }
  interval <- cut(vect,bins,dig.lab = 5)
  freq.table <- transform(table(interval))
  print(freq.table)
}
```


```{r}
sturge(rnorm(50,20,20))
```
```{r}
sturge(c(rep("A",10),rep("B",20),rep("C",15)))
```
```{r}
vect <- c(iris$Sepal.Length,iris$Sepal.Width,iris$Petal.Length,iris$Petal.Width)
sturge(vect)
```


